---
title: "Information on States of U.S"
author: "Saif Ul Mehdi"
date: "17/07/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## A Shiny Application

- The shiny application pitched in this presentation is (https://saif178.shinyapps.io/Project1/)

- The Shiny app source code is (https://github.com/Saif178/Course_Project)

## What does the app do?
- Allows you to visualise the population and life expectancy of US states in using the US State Facts and Figures dataset. 

- You can use sliders to select a population and life expectancy range to display and checkboxes to show different regions

- The output is an interactive map of the US showing the states that satisfy the selected criteria.

## Under the hood
```{r}
pop<-state.x77[,1]
lexp<-state.x77[,4]
states<-data.frame(state.name, pop, lexp, state.region,
                     hover=paste(state.name,':', 
                                  pop,lexp,'years',sep=' '))
states$hover<-as.character(states$hover)
```

- A data frame called `states` was created using the vectors from the US Facts and Figures Dataset.

- A fourth column (`hover`) was added for the interactivity of the map.

```{r, echo=TRUE, comment=''}
head(states)
```

## Output
- The slider values and checkbox values are used to filter the dataset using the `state.name` and `state.region` columns before creating the map.

- The output is a googlevis interactive map.

- The states turn green when they satisfy the selected criteria (slider and checkboxes)

- When each green state is hovered over, the name and area of the state is displayed.
